---
layout: post
comments: true
---



```{r setup, echo=FALSE, warning=F, message=FALSE}

## chunk options for this post
options(width=150)
knitr::opts_chunk$set(comment = NA) 
knitr::opts_chunk$set(fig.path='/images/prismaticR-intro-')

## load the libraries
library(RNeo4j)
library(pander)
library(stringr)
library(dplyr)
devtools::install_github("btibert3/prismaticR")
library(prismaticR)

## basic pander options
panderOptions("table.split.table", Inf)
panderOptions("table.style", "rmarkdown")


```


# Playing Around with the Prismatic Topic Graph API using R

The Prismatic Team has slowly been rolling out a very cool API.  You can read all about it [here](https://github.com/Prismatic/interest-graph).  At the same time, I have been using this as an opportunity to learn how to create an R package.  

After today's API update to identify the relevant content related to a specific topic, I wanted to highlight what is possible with a few lines of code using the `prismaticR` package.  Needless to say, my package is raw, but I wanted to demonstrate some of the cool things that you can do with Prismatic's API.  

## Let's get started

First things first, you can use `devtools` to install the `prismaticR` package.  

```{r echo=TRUE, eval=FALSE}
## install devtools package -- uncomment line below if you need to install
# install.packages("devtools")
library(devtools)

## install my prismaticR package if you havent already
install_github("btibert3/prismaticR")

## now lets load it
library(prismaticR)

```


Before you move forward, you will need to get an API token for your calls.  [You can get that token here](http://interest-graph.getprismatic.com/).

Store your token in an object called TOKEN ...

```{r eval=F}
TOKEN = "YOUR_TOKEN_HERE"
```

```{r echo=FALSE}
TOKEN = "MTQyMzQwOTM4MzUxOA.cHJvZA.YnRpYmVydDNAZ21haWwuY29t.Vz2n7Zd1ks8UZ4j9fDpU3MWVogk"
```


## Explore the API

The first thing that we should do is crawl the topic id database.  We will use this later ...

```{r warning=FALSE, message=FALSE}
tids = prizTID()

# ## keep everything lower case 
tids$topic = tolower(tids$topic)
```

We can use the `stringr` package to filter topic names based on keywords of interest.  For example, how many of the topics include the term `admission`   

```{r warning=FALSE, message=FALSE}
tids[str_detect(tids$topic, "admission"),]
```

A broader keyword ...

```{r warning=FALSE, message=FALSE}
tids[str_detect(tids$topic, "higher ed"),]
```

How about college?

```{r warning=FALSE, message=FALSE}
head(tids[str_detect(tids$topic, "college"),], 10)
```

And university? ..

```{r warning=FALSE, message=FALSE}
head(tids[str_detect(tids$topic, "university"),], 10)
```

And to close it out, how about student ... 

```{r warning=FALSE, message=FALSE}
tids[str_detect(tids$topic, "student"),]
```

This might be a good time to use the similar topic API.  To keep it simple, let's identify the topics that are related to the topic of `Harvard University` ...

```{r warning=F, message=F}
harvard = tids[str_detect(tids$topic, "harvard uni"),]$id
prizSIM(TOKEN, TID = harvard)
```

Interesting.  How about `Amherst College`? ...

```{r warning=F, message=F}
prizSIM(TOKEN, TID = 182)
```

The API even allows to identify the __current stories__ relevant to `college admissions`?  The top 5 are ...

```{r echo=F, warning=FALSE, message=F}
x = prizRECENT(TOKEN, 993)
x = arrange(x, desc(score))
```


```{r, echo=F}
x[1:5, c("score", "url")]
```


And for the sake of bots, here is the title of the "hottest" page above ...

```{r}
x_resp = html(x$url[1])
html_node(x_resp, "title") %>% html_text()
```


## Summary  

Have fun. I make no warantees for the R package, but with a few calls, you can do some really cool things.
